A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-09 docs/methods/erosion_methods.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a
range of scales found in nature, from large geological
formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down
to human-scale features and patterns~\cite{daerr2003erosion}. Though
less visible, these same forces are working at the very smallest scales,
slowly deteriorating the individual constituents of porous media
(e.g.~solid, sand, or clay) or biological structures like plaque and
biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we
develop numerical methods to simulate fluid-mechanical erosion of
multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.

Recent work in the high-Reynolds number regime has highlighted the
importance of the feedback between flow and morphology that occurs
during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013,
hewett2017evolution, moore2017riemann}; a similar feedback occurs in
the related processes of dissolution and melting~\cite{Huang2015,
kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
hewett2017pear, claudin2017dissolution}. In such cases, the flow alters
the shape of the immersed structures, which in turn modifies the
surrounding flow, and so on. Collectively, such processes have been
referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From
this viewpoint, the example of an eroding porous medium presents new
opportunities and challenges. For example, the medium itself is composed
of many solid constituents, so multi-body interactions, especially close
interactions, must be considered.
%Second, the long-range interactions
%facilitated by Stokes flow makes all the interactions between bodies important.

@@

% Point out complex shapes with sharp features, maybe polygonal.
% Point out channel structures develop.

@@

% Other possible refs for erosion: mit-spa2016, lachaussee2018competitive, lopez2018cfd
% Other possible refs for dissolution/melting: yuan2017dynamics, 
% Later, we can take out a lot of these references, especially ones that are cited elsewhere in the paper. For example, Mitchell and Spagnolie and several of my papers are cited elsewhere.
% Land formations, geophysical features, structures, patterns

% For groundwater flow, Darcy's law is often used, but this does not resolve the pore structure and assumes a homogeneous geometry which is often not valid. Instead, we use the incompressible Stokes equations as the governing fluid equations, and the individual pores are resolved which results in a complex multiply-connected geometry.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}. Though less visible, these same forces are working at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such examples, we develop in this paper numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in a Stokes flow---the most relevant regime for groundwater and the aforementioned bio-fluid applications.

Recent work in the high-Reynolds number regime has highlighted the importance of feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, as well as related processes such as dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion,
hewett2017pear, claudin2017dissolution}. 
In these cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on. Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. For example, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered.

@@

@@
